Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-21 Latex/tex/pr.tex
enhance code
enhance latex

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};

@@

$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals. 

@@

@@

$\phi$. So the total power can be represented as  

@@

In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power with the presence of constraints which is written as follow, 

@@

Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $. 

@@

To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into 

@@

Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration. Two different method is applied to acquire $\boldsymbol{A}$. The first method is using MOSEK and second method is a heuristic algorithm.

@@

\State Sort services according to their priority, the number of UEs in it and their requirements in descending order.
\State Sort slices according to the number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 

@@

\State Obtain Parameters of System

@@

where, $\mathfrak{y}_{u(v,i)}= (-\mu_{u(v,i)}+\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 

@@

$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} (\xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 

>>>>

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}};

@@

$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable illustrates whether slice $s$ is connected to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is connected to $s^{th}$ slice; otherwise, it is not connected.
\newline 

@@

Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not.

@@

$\phi$. So the total power of system for all active DCs that are connected to slices can be represented as  

@@

In this paper, the main goal is to simultaneously maximize sum-rate and minimize sum-power which is the total power of all RRHs and the total power consumption of baseband processing at all DCs with the presence of constraints which is written as follow, 

@@

Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ denotes the binary variable for connecting slices to services and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $ is a binary variable shown whether 
the a physical DC is connected to a VNFs of a slice or not. 

@@

To solve the problem and obtain $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into 

@@

Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration. Two different method is applied to acquire $\boldsymbol{A}$. 

@@

\State Sort services according to the number of UEs in it and their requirements in descending order.
\State Sort slices according to the weighted linear combination of number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 

@@

\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RRHs)

@@

where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 

@@

$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
